\chapter{Design Tasks}

This project requires a number of tasks to design the GUI.

\section{Preparatory Tasks}
\label{sec:prep}

Before GUI design can begin, the following tasks must be completed:

\begin{itemize}
    \item [A.] \label{task:A} Determine the target user. The target user of
        the application determines application functionality and gives a
        direction for visual style.
    \item [B.] \label{task:B} Gather user requirements and enumerate critical
        application functionality.
    \item [C.] \label{task:C} Determine required application screens.
    \item [D.] \label{task:D} Determine application screen flow.
    \item [E.] \label{task:E} Delegate required actions to each screen.
\end{itemize}

\section{GUI Design Tasks}
\label{sec:gui}

When sufficient information has been gathered to begin GUI design and the
preparatory tasks have been completed, our team will complete the following
tasks to design the GUI:

\begin{itemize}
    \item [F.] \label{task:F} Design the core restaurant reservation screen, with options for the
          user to specifiy number of people per reservation, reservation
          time, and the last name of the person making the reservation.
    \item [G.] \label{task:G} Design the search screen, with an option for a user to search for
          a restaurant either by name or by exploring a Google Maps screen.
    \item [H.] \label{task:H} Design an account creation screen, allowing new users to register
          for an account with the reservation system.
    \item [I.] \label{task:I} Design a sign in screen where registered users can sign in to
          their reservation system account.
    \item [J.] \label{task:J} Design an administraton screen where restaurant owners can add
          details about the types of reservations they will accept.
    \item [K.] \label{task:K} Design a comment and review screen where users can review the
          restaurants where they have made reservations.
\end{itemize}
